%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[13pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[utf8]{vietnam}
% adjust the page margins
\usepackage[scale=0.77]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
% \usepackage{hyperref}
% personal data
\name{Nguyễn}{Văn Huy}
\title{Man, 26 years old}                               % optional, remove / comment the line if not wanted
% \title{(updated May 13, 2021)}                               % optional, remove / comment the line if not wanted
\address{Yen Xa street, Tan Trieu ward, Thanh Tri district}{Hanoi City}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{(+84)~972~973~146}                   % optional, , remove / comment the line if not wanted
\email{huyhust13@gmail.com}                               %  remove / comment the line if not wanted

\begin{document}
\makecvtitle

\section{Career Objective}
\cvitem{}{Robots is my passion. I really want to become an expert in the field of robotics. Apply research results to benefit the community.}

\section{Knowledge \& Professonal skills}
\cvitem{}{Over 3 years experience in research and development of Autonomous Intelligent Mobile Robots}
% \cvitem{}{Experience in programming C++, Python, Microcontroller programming with Arduino}
\cvitem{}{Interested area: Autonomous Intelligent Mobile Robot, Manipulation Robot, Machine Learning, Deep Learning in Computer Vision, Smart Devices...}
\cvitem{}{Advanced skill in Python, $C/C^{++}$. Basic in Matlab, Mapple}
\cvitem{}{Familiar with Linux, Debian OS}
\cvitem{}{Knowledge of Git}
\cvitem{}{Experience in CAD design, 3D printer}

\section{Work experience}
\cventry{2020--present}{R\&D Engineer}{}{Meiko Automation}{}{
    \cvitem{\textit{AGV-AGF}}{Responsibility for research and development AGV/AGF.}
}
\cventry{2018--2020}{Researcher/Engineer}{}{CMC Institute of Science and Technology}{}{
\cvitem{\textit{Robotics:}}{Research and development in service robot, autonomous mobile robot.}
\cvitem{}{Apply ROS, SLAM into Mobile robot platform.}
\cvitem{\textit{Smart devices:} }{System integration. Developping GUI in Raspberry Pi for Face ID application.}
}
\section{Education}
\cventry{2018--2020}{Master}{Hanoi University of Science and Technology}{Hanoi}{\textit{Mechatronics}}{}
\cventry{2013--2018}{Bachelor}{Hanoi University of Science and Technology}{Hanoi}{\textit{Mechatronics}}{
    CPA: 3.56/4.0
}


\section{Publications}
\cvitem{2021}{Nguyen-Xuan H., Ngo-Thanh T., \textbf{Nguyen-Van H.} (2021) Development of an Autonomous Intelligent Mobile Robot Based on AI and SLAM Technology. Intelligent Systems and Networks. ICISN 2021. Lecture Notes in Networks and Systems, vol 243. \url{https://doi.org/10.1007/978-981-16-2094-2_40}}
\cvitem{2020}{Ha. Nguyen Xuan, \textbf{Huy. Nguyen Van}, \& Tung. Ngo Thanh. A New Landmark Detection Approach for Slam Algorithm Applied in Mobile Robot. Journal of Science \& Technology 146(2020), 31–36.}
\section{Awards}
\cvitem{2018}{Honda Y-E-S Awards 2018}
\cvitem{2017}{Bronze medal in National Olympic on Mechanics}
\cvitem{Scholaships}{Nitori scholarship, Euro Window scholarship}

\section{Languages}
\cvitemwithcomment{Vietnamese}{Native}{}
\cvitemwithcomment{English}{Intermediate}{}

\section{Others}
\cvitem{Habits}{Play sports: football, volleyball, running... }
\cvitem{Favorites}{Reading books (Lifestyfe, Personal Growth)}
\clearpage
\end{document}